\begin{center}

    \vspace*{2cm}

    {\textbf{Acknowledgements}}
    
    \vspace*{1cm}

\end{center}

This postgraduate study has been an extraordinary journey for me. I want to take this opportunity to express my appreciation to the individuals and institutions that have inspired, guided, supported and accompanied me along this way. I first want to thank my dissertation supervisor Dr. Bart de Keijzer. Dr. Keijzer has been very supportive throughout my dissertation work. Moreover, he inspires me that it takes courage to explore the unknown, and we should never forget to respect ourselves for that. Also, I want to thank my external supervisor Dr. Chrystalla Pavlou from TurinTech AI, for her patience and tirelessly support for all my queries. Her guidance paves the way for the completion of this report, and I cannot thank her enough for that.

In addition, I want to thank King's College London for fostering such an excellent, academically inclined environment from which I benefited greatly as a student. I am also immensely grateful to TurinTech AI for allowing me to work with some of the industry's brightest minds to extend the frontier of knowledge. In particular, I want to thank Dr. Lingbo Li and Dr. Buhong Liu for their exceptional coordination and for providing me with cutting-edge technology that makes my implementation of large-scale experiments possible.

I want to thank my cohorts in MSc Computational Finance, King's College London, for always being there for me and bringing out the best in me. Their companionship is a constant reminder to me that we are by no means alone, and we can always accomplish more together. Finally, I want to thank my family. Words cannot express how grateful I am for their unconditional support for me to pursue my dreams. They have shown and taught me the purest form of love I shall forever deem one of the most precious things I possess.

\newpage
